% Elliot Alladaye — CV (English)
% Self-contained: compiles with pdflatex using only base TeXLive packages.
\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[top=1.1cm,bottom=1.1cm,left=1.4cm,right=1.4cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{array}

\definecolor{accent}{HTML}{1F4E79}

\setlength{\parindent}{0pt}
\linespread{0.98}
\pagestyle{empty}

\titleformat{\section}
  {\Large\bfseries\color{accent}}{}{0pt}{}[\vspace{1pt}\hrule height 0.8pt\vspace{4pt}]
\titlespacing*{\section}{0pt}{5pt}{2pt}

\setlist[itemize]{leftmargin=1.4em,itemsep=0.5pt,topsep=1pt,parsep=0pt}

\newcommand{\entry}[2]{%
  \vspace{1pt}\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{#1} & #2 \\
  \end{tabular*}\par}

\newcommand{\subentry}[1]{\noindent\textit{#1}\par\vspace{1pt}}

\newcommand{\skillrow}[2]{\noindent\textbf{#1:}~#2\par\vspace{1pt}}

\begin{document}

% ===================== HEADER =====================
\begin{center}
  {\Huge\bfseries Elliot Alladaye}\\[3pt]
  {\large\color{accent} Backend \& AI Engineer}\\[5pt]
  \small
  \href{mailto:alladayeelliot@gmail.com}{alladayeelliot@gmail.com} ~$\bullet$~
  +33\,6\,XX\,XX\,XX\,XX ~$\bullet$~
  \href{https://www.linkedin.com/in/elliot-alladaye}{linkedin.com/in/elliot-alladaye}\\[2pt]
  Northern France / Belgium ~$\bullet$~ \textbf{Available full-time (CDI/CDD) from September 2026}
\end{center}
\vspace{2pt}

% ===================== PROFILE =====================
\section{Profile}
Backend \& AI engineer with 2 years of experience shipping production AI tooling for Digital Twins, covering the full AI-integration lifecycle: LLM orchestration, embeddings, retrieval, and anomaly detection. I build reliable, extensible systems with a strong bias toward data privacy and ownership. \textbf{MSc in Artificial Intelligence} (University of Kent, conferred Sept 2026); 5-year French engineering degree (Epitech) completed in 2027.

% ===================== EXPERIENCE =====================
\section{Experience}

\entry{Backend \& AI Engineer --- Stereograph}{Jul 2024 -- Aug 2025}
\subentry{Part-time then full-time}
\begin{itemize}
  \item Took an AI proof-of-concept to a production-ready product and maintained it alongside several other Python services.
  \item Built a \textbf{local-first RAG system} over clients' documents, keeping sensitive data off third-party APIs to guarantee privacy and data ownership.
  \item Shipped 3D-object anomaly detection that flagged modelling outliers automatically, reducing manual QA review time by \textasciitilde X\%.
  \item Migrated logging to \textbf{Datadog across 4 Python services}, reducing incident time-to-diagnose.
\end{itemize}

\entry{Full-stack \& AI Intern --- Stereograph}{Jul -- Dec 2023}
\subentry{Internship}
\begin{itemize}
  \item Built a chatbot (Python + ReactJS) embedded in Stereograph's BIM Digital-Twin software, enabling natural-language querying of building data.
  \item Created a text-driven interface for editing a Digital Twin's 3D view.
  \item Validated the technical feasibility of AI integration, earning a return offer to build out the product.
\end{itemize}

% ===================== PROJECTS =====================
\section{Projects}

\entry{Saver --- Tech Lead \& Sole Backend Engineer}{2023 -- present}
\subentry{Production-grade AI bookmarking platform (Python 3.13, FastAPI)}
\begin{itemize}
  \item Owned the \textbf{entire backend}---architecture, API, database, AI pipeline, security, and observability---for a service that ingests arbitrary URLs, extracts content, and auto-classifies it.
  \item Designed an async FastAPI + PostgreSQL/pgvector backend with \textbf{hybrid search} (weighted semantic cosine + full-text ranking) over a Mistral AI embedding and classification pipeline.
  \item Built a hardened auth layer: Argon2 hashing, JWT access tokens, and rotating refresh tokens with automatic token-family revocation on theft detection.
  \item Implemented \textbf{SSRF-safe} URL fetching (DNS pinning, per-redirect validation) across 15 platform extractors with a browser-impersonation fallback.
  \item Shipped end-to-end observability: structured logging through Fluentd $\rightarrow$ OpenTelemetry $\rightarrow$ Loki $\rightarrow$ Grafana, 5 dashboards as code; enforced strict \texttt{mypy} and a full async test suite.
\end{itemize}

\entry{AREA --- Automation Engine (Zapier-style)}{}
\begin{itemize}
  \item Built a microservices automation engine (Node.js + TypeScript), separating the API from background workers for modularity.
  \item Implemented a reliable RabbitMQ task queue with retry patterns, keeping workflows completing through transient failures.
\end{itemize}

% ===================== EDUCATION =====================
\section{Education}

\entry{MSc Artificial Intelligence --- University of Kent}{2025 -- 2026}
\subentry{Diploma conferred September 2026 --- international double-degree year of the Epitech program.}

\entry{Engineering Degree (Master's level), Software Engineering --- Epitech}{2022 -- 2027}
\subentry{5-year French \textit{Grande École} program; year abroad at the University of Kent. Diploma summer 2027.}

% ===================== SKILLS =====================
\section{Skills}
\skillrow{Languages}{Python, TypeScript, C/C++}
\skillrow{AI / ML}{LLM orchestration, embeddings \& RAG, anomaly detection; NumPy, Pandas, scikit-learn, TensorFlow}
\skillrow{Backend \& Infra}{FastAPI, PostgreSQL/pgvector, SQLAlchemy, REST APIs, ReactJS, Docker, Datadog, Grafana, Loki, OpenTelemetry}
\skillrow{Spoken}{French (native), English (bilingual)}

\end{document}
